---
title: "Analysis of search results"
author: "Per Møldrup-Dalum, AU"
format: html
editor: visual
---

# Loading libraries and setting up

```{r}
library(RCurl)
library(googlesheets4)
library(tidyverse)
library(tidytext)
library(here)
```

## get configurations

```{r}
google_sheet_url <- ""

source(here("configurations.R"))

# print configurations
google_sheet_url
```

# Load data

## Start with the Google sheet

```{r}
# Will need to authenticate to allow Tidyverse to access your google account.
# Need to manually select the "See, edit, create and delete all your Google Sheets spreadsheets. Learn more" option when authenticating.
search_results <-
  read_sheet(
    google_sheet_url,
    sheet = "Networks",
    skip = 0,
    col_types = "cccccccccccccccc"
  )
```

```{r}
glimpse(search_results)
```

## Now load the world population data

```{r}
API_SP_POP_TOTL_DS2_en_csv_v2_4770387_modified <- read_csv(
  here("data/API_SP/API_SP.POP.TOTL_DS2_en_csv_v2_4770387-modified.csv"),
  col_types = cols(`1960` = col_double()))
```

```{r}
glimpse(API_SP_POP_TOTL_DS2_en_csv_v2_4770387_modified)
```

## Combine the population with the search results

```{r}
search_results |>
  left_join(
    API_SP_POP_TOTL_DS2_en_csv_v2_4770387_modified |>
      select(`Country Code`, `Country Name`, `2021`), by="Country Code") -> search_results_pop
```

Create a table of country names and country codes

```{r}
countries <- API_SP_POP_TOTL_DS2_en_csv_v2_4770387_modified |>
  select(`Country Name`, `Country Code`)
```


# Counting terms in the Target groups and Competency columns

Target group (self-identification)

```{r}
search_results |> 
  select(`Target group (self-identification)`) |> 
  unnest_tokens(
    target_groups,
    `Target group (self-identification)`, 
    token="lines") |> 
  count(target_groups) |> 
  arrange(desc(n)) |> 
  print(n=140)
```

Competences

```{r}
search_results |> 
  select(`Competences`) |> 
  unnest_tokens(competency,Competences, token="lines") |>  
  count(competency) |> 
  arrange(desc(n)) |> 
  print(n=130)
```

## Competencies

```{r}
# search_results |> 
#     select(`Competences`) |> 
#     mutate(`Competences` = str_replace_all(`Competences`, ",","\n")) |>
#     unnest_tokens(competency,Competences, token="lines") |> mutate(competency = str_trim(competency)) |>   
#     #filter(str_detect(competency,"fair")) |>
#     count(competency) |>
#   arrange(desc(n)) |> 
#   googlesheets4::write_sheet(
#     ss = google_sheet_url,
#     sheet = "Competencies (auto generated)"
#   )
```

We have too many terms for the same ting... e.g. fair:

```{r}
search_results |> 
    select(`Competences`) |> 
    mutate(`Competences` = str_replace_all(`Competences`, ",","\n")) |>
    unnest_tokens(competency,Competences, token="lines") |> mutate(competency = str_trim(competency)) |>   
    filter(str_detect(competency,"fair")) |>
    count(competency)
```

Tokenize competenzies

```{r}
search_results |>
  select(`Competences`) |>
  mutate(`Competences` = str_replace_all(`Competences`, ",", "\n")) |>
  unnest_tokens(competency, Competences, token = "lines") |>
  mutate(competency = str_trim(competency)) |>
  group_by(competency) |>
  summarise(n = n()) |>
  arrange(desc(n)) -> search_results_tokens
```


## A Wordcloud

```{r}
#install.packages("wordcloud")
library(wordcloud)
#install.packages("RColorBrewer")
library(RColorBrewer)
#install.packages("wordcloud2")
library(wordcloud2)
```

```{r}
wordcloud(
  words = search_results_tokens$competency,
  freq = search_results_tokens$n,
  min.freq = 1,
  max.words = 200,
  random.order = FALSE,
  #rot.per = 0.35,
  colors = brewer.pal(8, "Dark2")
)
```
```{r}
wc<-wordcloud2(search_results_tokens)
```

Get PNG of Europe from https://commons.wikimedia.org/wiki/File:Europe_map.png

```
$ magick Europe_map.png -fuzz 40%  -fill black -opaque blue  europe.png
```

```{r}
wordcloud2(
  search_results_tokens,
  figPath = "europe.png",
  ellipticity = .9,
  gridSize = 10,
  #color = c_trim,
  backgroundColor = "white"
)

```

```{r}
library(htmlwidgets) 
#install.packages("webshot")
#webshot::install_phantomjs()
saveWidget(wc,"competencies.html",selfcontained = F)
webshot::webshot("competencies.html","competencies.png",vwidth = 1992, vheight = 1744, delay =10)
```


# Some visualisations

```{r}
library(ggthemes)
```

## Count networks per nation

```{r}
non_national <- search_results_pop |>
  filter(`Country Code` == "international" | `Country Code` == "regional") |> 
  pull(`Country Code`) |> length()

search_results_pop|> 
  filter(`Country Code` != "international" & `Country Code` != "regional") |> 
  group_by(`Country Name`,`2021`) |>
  summarise(pop=max(`2021`),sum=n(), adjusted=1e6*sum/pop) |>
  select(`Country Name`, sum) |>
  ggplot() +
    geom_col(aes(x=`Country Name`, y=sum)) +
    coord_flip() +
    labs(
      title = "Number of found networks",
      caption = "Source: REF TO COLLECTED DATA and REF TO WORLD DATA BANK",
      subtitle = str_c("found ", non_national," regional or international not included")
    ) +
    ylab("") +
    xlab("") +
    scale_y_continuous(breaks=c(0,1,2,5,10,15,20,25), minor_breaks = NULL) +
    theme_light()

ggsave(here("output","count-per-country.png"))
```

### Adjustet count by population

```{r}
non_national <- search_results_pop |>
  filter(`Country Code` == "international" | `Country Code` == "regional") |> 
  pull(`Country Code`) |> length()

search_results_pop|> 
  filter(`Country Code` != "international" & `Country Code` != "regional") |> 
  group_by(`Country Name`,`2021`) |>
  summarise(pop=max(`2021`),sum=n(), adjusted=1e6*sum/pop) |>
  select(`Country Name`, adjusted) |>
  ggplot() +
    geom_col(aes(x=`Country Name`, y=adjusted)) +
    coord_flip() +
    labs(
      title = "Number of found networks per million people",
      caption = "Source: REF TO COLLECTED DATA and REF TO WORLD DATA BANK",
      subtitle = str_c("found ", non_national," regional or international not included")
    ) +
    ylab("") +
    xlab("") +
    scale_y_continuous(breaks=c(0,1,2,3,4,5,6,7), minor_breaks = NULL) +
    theme_light()
ggsave(here("output","count-per-country-per-million.png"))
```

## Spread of competences



## Age

```{r}
year_scale <- c(
  "2020",
  "2018",
  "1971",
  "2019",
  "2021",
  "2022",
  "2009",
  "NA",
  "2013",
  "2014",
  "2017",
  "2011",
  "2016",
  "2008",
  "2012",
  "2015",
  "2005",
  "earlier than 2019")

no_year <- search_results |> 
  filter(is.na(`Year of establishment`)) |> 
  pull(`Year of establishment`) |> 
  length()

search_results_pop |> 
  filter(!is.na(`Year of establishment`)) |> 
  mutate(age = 2023 - as.numeric(`Year of establishment`)) |>
  #count(Country) |> 
  #filter(str_detect(`Year of establishment` ,"^\\d*$")) |>
  #mutate(yl=length(`Year of establishment`)) |>
  #select(`Year of establishment`)
  #select(yl)
  ggplot() +
    geom_bar(aes(x=age)) +
    #coord_flip() +
    labs(
      title = "Age of found networks",
      caption = "Source: REF TO COLLECTED DATA and REF TO WORLD DATA BANK",
      subtitle = str_c("found ",no_year," without year of establisment)")
    ) +
    ylab("Count") +
    xlab("Age") +
    scale_x_continuous(breaks=c(1,3,5,10,15,20,50,75,100), minor_breaks = NULL) +
    theme_light()

ggsave(here("output","age.png"))
```
```{r}
search_results_pop |> 
  filter(!is.na(`Year of establishment`)) |> 
  mutate(age = 2023 - as.numeric(`Year of establishment`)) |>
  filter(age < 21) |>
  #count(Country) |> 
  #filter(str_detect(`Year of establishment` ,"^\\d*$")) |>
  #mutate(yl=length(`Year of establishment`)) |>
  #select(`Year of establishment`)
  #select(yl)
  ggplot() +
    geom_bar(aes(x=age)) +
    #coord_flip() +
    labs(
      title = "Age of found networks younger than 21",
      caption = "Source: REF TO COLLECTED DATA and REF TO WORLD DATA BANK",
      subtitle = str_c("found ",no_year," without year of establisment)")
    ) +
    ylab("Count") +
    xlab("Age") +
    scale_x_continuous(breaks=c(1,3,5,10,15,20,50,75,100), minor_breaks = NULL) +
    theme_light()

ggsave(here("output","age-21.png"))
```



















########################################################################
########################################################################
# old stuff
########################################################################
########################################################################

```{r}
search_results |> 
  select(`Year of establishment`)
```

```{r}
year_scale <- c(
  "2020",
  "2018",
  "1971",
  "2019",
  "2021",
  "2022",
  "2009",
  "NA",
  "2013",
  "2014",
  "2017",
  "2011",
  "2016",
  "2008",
  "2012",
  "2015",
  "2005",
  "earlier than 2019")

no_year <- search_results |> 
  filter(is.na(`Year of establishment`)) |> 
  pull(`Year of establishment`) |> 
  length()

search_results |> 
  filter(!is.na(`Year of establishment`)) |> 
  mutate(`Year of establishment` = if_else(`Year of establishment` == "earlier than 2019","2019 (Before)",`Year of establishment`)) |> 
  #count(Country) |> 
  #filter(str_detect(`Year of establishment` ,"^\\d*$")) |>
  #mutate(yl=length(`Year of establishment`)) |>
  #select(`Year of establishment`)
  #select(yl)
  ggplot() +
    geom_bar(aes(x=`Year of establishment`)) +
    coord_flip() +
    ylab(str_c("Number of found networks (found ",no_year," without year of establisment")) +
    scale_y_continuous(breaks=c(0,1,2,5,10,15)) +
    theme_light()
```

# Ideer

1.  tilføj antal indbyggere i landene

[World population](https://data.worldbank.org/indicator/SP.POP.TOTL?end=2021&start=2021&view=map)

illustrer competencies

noget geo-plot?

kan der lavet noget netværk analyse?

TF-IDF på description og activities

age?

age combined with activities

description, activities, competencies

1\<n\<=3: reginal

n\>3: internaional

WILD IDÉ: wget alle websites og lav rigtig netværksanalyse af det resultat!!


```{r}
search_results |> 
  select(`Target group (self-identification)`) |> 
  unnest_tokens(lines,`Target group (self-identification)`, token="lines") |>
  count(lines) |>
  arrange(desc(n)) |> 
  mutate(target_group = str_sub(lines,end=40)) |> 
  select(-lines)
```
